Manuscript plots

### 2025-02-20 manuscript_modelling_and_plots.Rmd
adding notes on conditional effects for individuals

@@

In the code chunk above (and the same for the gaze transitions entropy model), I am calculating the conditional effects for the existing groups in the dataset. I do this by extracting the model parameter estimates however in other tutorials (https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#conditional-effects-for-existing-groups) they use a different method. Overall, the mean value of the conditional effect is identical. However in the Heiss tutorial, each estimate is accompanied by a 95% HDIs for each individual. This might prove useful for further analysis if needed, but it not used in the current manuscript.

To illustrate the equivalence, I'll use the Heiss method below.

>>>>

# load model
sge.fit.3 <- readRDS(here::here("gaze_entropy_heterogenous/models/sge_fit_3.rds"))

@@

In the code chunk above (and the same for the gaze transitions entropy model), I am calculating the conditional effects for the existing groups in the dataset (AKA what is the effect of N-back on gaze entropy for each individual).

I do this by extracting the random effects parameter estimates directly from the model, and adding the conditional mode to the average effect. In other tutorials (https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#conditional-effects-for-existing-groups) they use a different method with the emmeans functions. Overall, the mean value of the conditional effect is identical. However in the Heiss tutorial, each estimate is accompanied by a 95% HDIs for each individual. This might prove useful for further analysis if needed, but it not used in the current manuscript.

To illustrate the equivalence, I'll use the Heiss method below. When viewed with the View() function, the average for each participant is the same as the method above.
